PeerMind: Towards Collective Decision-Making

### 2016-11-29 paper.tex
Range voting.

\subsection{Statistical Quorum}

\subsubsection{Background}
A population of voters needs to collectively decide which item (if any) to take action on out of a set of competing items.
In order to democratically take action, the population needs to have a \{simple, super\}-majority of ``yes'' votes on a
winning item, while also demonstrating that the winning item is preferred over all other competing items.
We do not want to poll the entire population, but we do want to be certain (specifically, $99\%$ certain) that
the population does not take undesired actions, which in this case encompasses taking action on an item that is not
supported by a majority of the population and/or taking action on an item that is not clearly preferred over all
other competing alternatives.

@@

\subsection{Score Voting}

\todo[inline]{Do we take into the account the distribution of votes? So if you have a very large standard deviation
we might want to prefer a decision less than some other decision with smaller standard deviation, but maybe
also smaller (but still positive) average. Is distribution of votes influencing dynamic quorum?}

>>>>

\subsection{Range Voting}

Range voting (score voting) is voting where members of a community express their positions on open proposals by assigning
each a score on a fixed scale, in the context of this paper, between $-1$ and $+1$.
Prior work has shown that this approach generalizes many previous approaches to voting and allows members to express their
positions in a highly informative and precise manner.
We find it especially suitable for a web application because many web users are used to use it when ranking products
and giving other ``five-star'' feedback.
Moreover, if later on a new proposal is added to a set of existing proposals on which voting was already open, only the
new proposal needs to be evaluated by members, as opposed to alternative voting systems where the relative rankings of
each proposal would need reassessing (assuming members use a consistent personal scale when voting).

\subsection{Dynamic Quorum}

\subsubsection{Background}
A population of voters (a community) needs to collectively decide which item (if any) to take action on out of a set of competing items.
In order to democratically take action, the population needs to have a \{simple, super\}-majority of ``yes'' votes on a
winning item, while also demonstrating that the winning item is preferred over all other competing items.
We do not want to poll the entire population, but we do want to be certain (specifically, $99\%$ certain) that
the population does not take undesired actions, which in this case encompasses taking action on an item that is not
supported by a majority of the population and/or taking action on an item that is not clearly preferred over all
other competing alternatives.

@@

%\todo[inline]{Do we take into the account the distribution of votes? So if you have a very large standard deviation
%we might want to prefer a decision less than some other decision with smaller standard deviation, but maybe
%also smaller (but still positive) average. Is distribution of votes influencing dynamic quorum?}
